### 2020-10-22 thesis/chap_1.tex
comment 13 about buffer details

The first step consisted in reclassifying the AAFC land use dataset into 4 categories: the 3 categories of our land use change model plus roads and wetlands. Then we aggregated the rasters by a factor of 3 (using the mode of the neighborhood, changing the resolution to 90m). We applied this aggregation to all rasters (for continuous data we used the mean and not the mode). This allowed us to reduce run time as well as memory requirements. Roads were removed during aggregation: this was necessary as the process tends to break them up, creating holes in them. Major roads from the Adresses Quebec dataset were rasterized and patched on top of the resulting maps. Then, all the pixels classified as forest were reclassified as null, and the resulting maps were patched with the forest cover from the LANDIS simulations' starting conditions (state of forest types in 2010). Some cells remained null as the forest cover in 1990 was larger than that of 2010. We filled those NULL values using modal imputation under two different neighbourhood window sizes (13 and 25 pixels). Next, a 5km buffer was added around Montérégie so as to improve the Circuitscape results later down the pipeline (see the Connectivity Analysis section). Not all NA cells were due to the difference in forest cover between 1990 and 2010, some were due to the fact that the LANDIS run did not cover some parts of the 5km buffer. Those cells were filled with the value corresponding to the forest type Mixed Forest of Medium Age. We decided on this imputed value because it is among the most suitable for all species and therefore unlikely to cause significant changes in the Circuitscape runs, even if it does not correspond to the mode or the mean for the region. In addition, because no change takes place in the buffer, those values can be equivalent to a "padding" around the landscape.

>>>>

The first step consisted in reclassifying the AAFC land use dataset into 4 categories: the 3 categories of our land use change model plus roads and wetlands. Then we aggregated the rasters by a factor of 3 (using the mode of the neighborhood, changing the resolution to 90m). We applied this aggregation to all rasters (for continuous data we used the mean and not the mode). This allowed us to reduce run time as well as memory requirements. Roads were removed during aggregation: this was necessary as the process tends to break them up, creating holes in them. Major roads from the Adresses Quebec dataset were rasterized and patched on top of the resulting maps. Then, all the pixels classified as forest were reclassified as null, and the resulting maps were patched with the forest cover from the LANDIS simulations' starting conditions (state of forest types in 2010). Some cells remained null as the forest cover in 1990 was larger than that of 2010. We filled those NULL values using modal imputation under two different neighbourhood window sizes (13 and 25 pixels). Next, a 5km buffer was added around Montérégie so as to improve the Circuitscape results later down the pipeline. This buffer was created by keeping land use data in a 5km radius around Montérégie. Not all NA cells were due to the difference in forest cover between 1990 and 2010, some were due to the fact that the LANDIS outputs did not cover some parts of that 5km buffer. Those cells were filled with the value corresponding to the forest type Mixed Forest of Medium Age. We decided on this imputed value because it is among the most suitable for all species and therefore unlikely to cause significant changes in the Circuitscape runs, even if it does not correspond to the mode or the mean for the region. In addition, because no change takes place in the buffer, those values can be equivalent to a "padding" around the landscape.
